Individual ABC Fits

### 2024-01-23 Model/abc_hier.qmd
model tables and general processing

@@

#ind_fits <- ind_fits |> list_assign(runInfo = zap())
# names(ind_fits)
# names(ind_fits$id_fits_alm_varied)
# names(ind_fits$id_fits_alm_varied[[1]])

#teter_results_df <- imap_dfr(ind_fits, ~imap_dfr(.x, ~.x[["teter_results"]] ,.id="id"))

@@

post_dat <- ind_fits_df |> 
  select(sim_dat,rank) |> unnest(sim_dat) |> filter(expMode2=="Test") |>
  group_by(id,condit,x) |>
  mutate(avg_y=mean(y)) |> 
  relocate(id,condit,Model,Fit_Method,expMode2,tr,rank,c,lr,x,y,avg_y)

@@

id1 <- ind_fits_df |> filter(id %in% ids2) 
names(id1)
typeof(id1$sim_dat)
str(id1$sim_dat[[1]])
id1 <- id1 |> select(rank,sim_dat) |> unnest(sim_dat) |>filter(rank<=2)

@@

>>>>

---
title: Individual ABC Fits
author: Thomas Gorman
date: "`r Sys.Date()`"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

@@

post_dat <- ind_fits_df |> 
  select(sim_dat,rank) |> unnest(sim_dat,names_repair = repair_names) |> filter(expMode2=="Test") |>
  group_by(id,condit,x) |>
  mutate(avg_y=mean(y)) |> 
  relocate(id,condit,Model,Fit_Method,expMode2,tr,rank,c,lr,x,y,avg_y)

@@

@@

##  Posterior Average Table: 
```{r fig.width=12, fig.height=17}
#| eval: true
post_tabs <- abc_tables(post_dat_l)
post_tabs$et_sum |> gt::gt()

post_tabs$et_sum |> select(condit,Fit_Method,Avg_ALM_error, Avg_EXAM_error) |> filter(Fit_Method=="Test")

## Distributions: 
```{r, fig.width=12, fig.height=15}
#| eval: true
plot_sampled_posterior(ind_fits)
plot_indv_posterior(ind_fits_df)

## Distributions: 
```{r, fig.width=12, fig.height=15}
#| eval: true
plot_sampled_posterior(ind_fits)
plot_indv_posterior(ind_fits_df)

## Posterior Predictive: 
```{r, fig.width=12, fig.height=14}
#| eval: true
group_predictive_plots(post_dat_l)
group_best_plots(post_dat_l)
```

## Individual Plots:
```{r, fig.width=12, fig.height=17}
#| eval: true
indv_best_plots(post_dat_l)
indv_predictive_plots(post_dat_l, ids2)
indv_predictive_plots(post_dat_l, idsBad)

## Bigger Tables:
```{r}
#| eval: true

post_tabs$et_sum_x |> kable()

post_tabs$et_sum_x_indv |> kable()
```
